Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2017-11-10 2017-EUROPAR/Gamification/paper.tex
Adding to related work refs #2

Volunteer computing involves users who decide to run a program that acts
as a client or as a peer in a distributed computing experiment
and, as such, has been deployed in many different ways since the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}, which used
a client that acted as an screensaver, or a
high-throughput queuing system such as HTCondor \cite{HTCondor}.
However,
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as both an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15anom}. Systems based on the
JavaScript/browser combination
emphasize the ephemerality, ease of use, and universality, while
systems such as HTCondor or BOINC might be more adequate for work that % citation for BOINC (?)
requires higher availability of volunteer resources. In order to increase availability, systems rely on downloadable clients, and in some cases like HTCondor, they also require administrative access to certain resources.

@@

Next we will present the gamification technique used in this experiment.

>>>>

Volunteer computing involves users who decide to run a program that acts
as a client or as a peer in a distributed computing experiment
and, as such, has been deployed in many different ways since the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}, which used
a client that acted as an screensaver, or a
high-throughput queuing system such as HTCondor \cite{HTCondor}.
However,
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as both an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks in what is generally described as BBVC or Browser-Based
Volunteer Computing \cite{fabisiak2017browser}. Systems based on the
JavaScript/browser combination
emphasize the ephemerality, ease of use, and universality, while
systems such as HTCondor or BOINC \cite{boinc_grid04} might be more adequate for work that 
requires higher availability of volunteer resources. In order to
increase availability, systems rely on downloadable clients, and in
some cases like HTCondor, they also require administrative access to
certain resources. In fact, Fabisiak \cite{fabisiak2017browser}
analyzes the different capabilities of Internet and browser-based
systems, including their ability to handle large sets of input data
and time-consuming problems, concluding that BBVC is mostly apt for
short, data-light tasks. This recent survey does not analyze the
impact of gamification as we do in this paper, which might help in
this area.

@@

Next we will present the gamification technique used in this
experiment, using a system whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15anom}.
